%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt, a4paper]{awesome-cv-fa5}

\geometry{left=1.35cm, top=.8cm, right=1.35cm, bottom=1.8cm, footskip=.5cm}

\colorlet{awesome}{awesome-red}
\setbool{acvSectionColorHighlight}{true}

\hfuzz=2.5pt
\hbadness=10000
\renewcommand{\acvHeaderSocialSep}{\,\textbar\,}

\name{Denis}{Evsyukov}
\position{Backend Developer{\enskip\cdotp\enskip}Go Engineer}
\address{Moscow, Russia}

\mobile{+7 (926) 622-67-27}
\email{denis@evsyukov.org}
\homepage{denis.evsyukov.org}
\github{juev}

\begin{document}

\makecvheader[C]

\makecvfooter
  {\today}
  {Denis Evsyukov~~~·~~~Resume}
  {\thepage}

\cvsection{Summary}

\begin{cvparagraph}
Backend Developer with 10+ years in IT and 5+ years of Go development. Built high-load systems at VK, Ozon, and Tinkoff. Strong background in Kubernetes, microservices architecture, and real-time communications. Experienced in building scalable distributed systems, implementing message-driven architectures, and working with cloud-native technologies.
\end{cvparagraph}

\cvsection{Experience}

\begin{cventries}

  \cventry
    {Golang Developer}
    {VK}
    {Moscow, Russia}
    {Oct. 2025 -- Present}
    {
      \begin{cvitems}
        \item {Building real-time multiplayer backend for mini-games platform}
        \item {Implementing WebSocket communication with low-latency state synchronization}
        \item {Designing scalable architecture to serve VK's massive user base}
        \item {Optimizing game session management and player matchmaking}
      \end{cvitems}
    }

  \cventry
    {Golang Developer}
    {Flant}
    {Moscow, Russia}
    {Jun. 2024 -- Oct. 2025}
    {
      \begin{cvitems}
        \item {Developed modules and hooks for Deckhouse Kubernetes Platform}
        \item {Built Kubernetes operators and custom integrations}
        \item {Worked extensively with Kubernetes API, CRDs, and controllers}
        \item {Implemented infrastructure automation for enterprise clients}
      \end{cvitems}
    }

  \cventry
    {Golang Developer}
    {Samokat (Megamarket)}
    {Moscow, Russia}
    {Sep. 2023 -- Jun. 2024}
    {
      \begin{cvitems}
        \item {Built backend services for Megamarket storefront platform}
        \item {Developed RESTful APIs for product catalog and ordering system}
        \item {Implemented integrations with external logistics and payment providers}
        \item {Optimized database queries for high-traffic e-commerce scenarios}
      \end{cvitems}
    }

  \cventry
    {Golang Developer}
    {Ozon}
    {Moscow, Russia}
    {Nov. 2021 -- Sep. 2023}
    {
      \begin{cvitems}
        \item {Developed high-load notification services (Push/SMS/Email)}
        \item {Implemented Kafka-based asynchronous message processing pipeline}
        \item {Scaled system to handle millions of notifications daily}
        \item {Built monitoring and alerting for critical communication services}
      \end{cvitems}
    }

  \cventry
    {Senior Engineer / DevOps}
    {Tinkoff}
    {Moscow, Russia}
    {Sep. 2017 -- Nov. 2021}
    {
      \begin{cvitems}
        \item {Prepared Ansible playbooks for server and service administration}
        \item {Developed infrastructure management tools in Go}
        \item {Automated software development and testing using Jenkins, Maven, Gradle}
        \item {Administered RabbitMQ and Consul clusters}
        \item {Organized monitoring with Zabbix, Prometheus, and Grafana}
      \end{cvitems}
    }

  \cventry
    {Senior Release Engineer}
    {Netcracker}
    {Tolyatti, Russia}
    {Jan. 2013 -- Oct. 2017}
    {
      \begin{cvitems}
        \item {Automated software development and testing using Jenkins, Maven, Gradle}
        \item {Set up monitoring infrastructure with Zabbix, Prometheus, Grafana}
      \end{cvitems}
    }

\end{cventries}

\cvsection{Technical Skills}

\begin{cvskills}

  \cvskill
    {Languages}
    {Go (5+ years), Python, Bash}

  \cvskill
    {Databases}
    {PostgreSQL, MySQL, Redis, MongoDB}

  \cvskill
    {Message Brokers}
    {Kafka, RabbitMQ, NATS}

  \cvskill
    {Protocols}
    {gRPC, REST, WebSocket, GraphQL}

  \cvskill
    {Infrastructure}
    {Kubernetes, Docker, Helm, Werf, Terraform}

  \cvskill
    {CI/CD}
    {GitHub Actions, Jenkins, GitLab CI}

  \cvskill
    {Monitoring}
    {Prometheus, Grafana, Zabbix, Jaeger}

\end{cvskills}

\cvsection{Open Source Projects}

\begin{cvhonors}

  \cvhonor
    {gobrew}
    {Go version manager written in Go}
    {411 stars}
    {}

  \cvhonor
    {starred}
    {Awesome List generator from GitHub stars}
    {33 stars}
    {}

  \cvhonor
    {tor-relay-scanner-go}
    {Tor relay availability checker}
    {21 stars}
    {}

\end{cvhonors}

\cvsection{Education}

\begin{cventries}

  \cventry
    {Bachelor of Commerce (BCom)}
    {International Market Institute (IMI)}
    {Moscow, Russia}
    {2007 -- 2009}
    {}

  \cventry
    {Bachelor of Education (BEd)}
    {Tolyatti State University}
    {Tolyatti, Russia}
    {1997 -- 2002}
    {}

\end{cventries}

\cvsection{Languages}

\begin{cvskills}

  \cvskill
    {Russian}
    {Native Speaker}

  \cvskill
    {English}
    {Pre-Intermediate (Reading technical documentation)}

\end{cvskills}

\end{document}
